---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = F,
  warning = F
)
```

# corpuscleaner

<!-- badges: start -->
<!-- badges: end -->

This package has a collection of 18 Documents cleaned and ready for use regarding Corpus Analysis. It has `novels()` function which has the collection consisting of: 

* `title`: The Title of the Document
* `text`: The Text of the Document
* `year`: The Year the Document was Published
* `author`: The Author of the Document
* `novel_bookshelf`: The Category of the Document

It also has a function `polish(..., vars)` that consists of: 

* `title`
* `text` 

and can add any `column_name` of your choice such as `year`, `author`, or both. 

## Installation

You can install the development version of corpuscleaner from [GitHub](https://github.com/) with:

``` r
# install.packages("corpuscleaner")
# devtools::install_github("anshalmm/R-Projects")
```

## Examples

These are basic examples of what `corpuscleaner` can show you when combined with basic text analysis:

```{r example}
library(corpuscleaner)
library(dplyr)
library(tidytext)
```

Here we're using the `novels()` function and filtering it out to find the metadata of the document `Wuthering Heights`


```{r}
WH_Text = novels() %>%
  filter(title == "Wuthering Heights")

WH_Text
  
```


Then we can use the `polish` function to extract the title, text, and an additional column, author for the 
document `Vathek`.

We can do some frequency list text analysis on this document by finding all the unigrams in it:


```{r}
polish(title == "Vathek", vars = "author")
unigram_Analysis = polish(title == "Vathek", vars = "author")

UA = unigram_Analysis %>%
  unnest_tokens(word, 
                text, 
                token = "words") %>%
  anti_join(get_stopwords("en", source = "smart")) 

UA_Count_Words = UA %>%
  count(word, sort = T)
UA_Count_Words

```


If you would like to know how to use this package, please see the Vignette on it. 
